The title

### 2020-09-02 manuscript/manuscript.Rmd
add plots

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

```{r setup, include = FALSE}
# Load packages
library(papaja)
library(reticulate)
library(MASS)
library(Matrix)
library(lme4)
library(buildmer)
library(emmeans)
library(magrittr)
library(tidyverse)

# Chunk options
knitr::opts_chunk$set(include = FALSE, echo = FALSE)

# Specify conda environment for Python
use_condaenv("r-reticulate", required = TRUE)

@@

@@

# Define parameters for preprocessing
preproc_params = dict(n_components=15, method='fastica',           # ICA parameters
                      l_freq=0.1, h_freq=30,                       # Filter edges
                      event_id={'match': 221, 'mismatch': 222},    # EEG triggers
                      tmin=-0.5, tmax=1.498,                       # Length of epochs
                      baseline=(-0.2,0))                           # Baseline correction
reject = dict(eeg=200e-6)                                          # Rejection threshold

# # Debug
# locals().update(preproc_params)
# vhdr_fname = 'data/exp1/EEG/Vp0001.vhdr'

# Define preprocessing function
def preproc(vhdr_fname, n_components, method, l_freq, h_freq, event_id, tmin, tmax, baseline):
  # Load EEG data
  raw = mne.io.read_raw_brainvision(vhdr_fname, preload=True)
  # Create new virtual EOG channels
  raw = mne.set_bipolar_reference(raw, 'Auge_u', 'Fp1', ch_name='VEOG', drop_refs=False)
  raw = mne.set_bipolar_reference(raw, 'F9', 'F10', ch_name='HEOG', drop_refs=False)
  raw.set_channel_types(mapping={'VEOG': 'eog', 'HEOG': 'eog'})
  # Add EasyCap electrode layout, removing any excessive channels
  montage = mne.channels.make_standard_montage('easycap-M1')
  raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(['VEOG', 'HEOG'])))
  raw.set_montage(montage=montage)
  # Re-reference to common average
  raw, _ = mne.set_eeg_reference(raw, 'average')
  # Run ICA on a copy of the data
  filt_raw = raw.copy()
  filt_raw.load_data().filter(l_freq=1, h_freq=None)
  ica = mne.preprocessing.ICA(n_components=n_components, random_state=12345, method=method)
  ica.fit(filt_raw)
  # Remove bad components based on correlations with EOG
  eog_indices, eog_scores = ica.find_bads_eog(raw)
  ica.exclude = eog_indices
  raw = ica.apply(raw)
  # Apply band-pass filter
  raw = raw.filter(l_freq=l_freq, h_freq=h_freq)
  # Epoching including baseline correction
  events, _ = mne.events_from_annotations(raw, verbose=False)
  epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax,
                      baseline=baseline, preload=True)

  # # Autoreject                    
  # import autoreject
  # 
  # ar = autoreject.AutoReject(thresh_method='random_search', verbose=False)
  # epochs_clean = ar.fit_transform(epochs)
  # 
  # rejected = epochs_clean.drop_log
  # rejected[:] = [item for item in rejected if item != ['IGNORED']]
  # rejected = [i for i in range(len(rejected)) if rejected[i] != []]
  # 
  # ransac = autoreject.Ransac(verbose=False)
  # epochs = ransac.fit_transform(epochs)
  # 
  # reject = autoreject.get_rejection_threshold(epochs)

@@

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists('output/exp1-epo.fif'):
  # Load preprocessed data from file
  epochs_exp1 = mne.read_epochs('output/exp1-epo.fif', preload=True)
else:
  # Actually apply the preprocessing function
  epochs_exp1 = [preproc(fname, **preproc_params) for fname in fnames_exp1]
  # Combine into a single data set
  epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
  # Backup epochs to the export folder
  epochs_exp1.save('output/exp1-epo.fif')

# Get indices of bad epochs despite ICA
rej_exp1 = epochs_exp1.copy().drop_bad(reject=reject).drop_log
rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
```

```{r exp1-analysis}
# Define function for processing behavioral data
preproc_behav <- function(txt_fname){
  # Read log file
  dat <-  suppressMessages(suppressWarnings(read_tsv(txt_fname)))
  # Remove filler stimuli (well-known objects)
  dat %<>% filter(bek_unbek != "bekannt")
  # Add a column for the part of the experiment
  dat %<>% mutate(part = as_factor(Wdh - 210))

  # Assign stimuli to conditions based on keywords and button presses
  known <- dat %>% filter(part == "1" & Tastencode == 201) %>% pull(StimID)
  insight <- dat %>%filter(part == "2" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>% pull(StimID)
  naive <- dat %>% filter(part == "2" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>% pull(StimID)
  dat %<>% mutate(condition = as_factor(case_when(StimID %in% known ~ "Known",
                                                  StimID %in% insight ~ "Insight",
                                                  StimID %in% naive ~ "Naive")))
  # Remove unrealistically short RTs
  dat %<>% mutate(RT = replace(RT, RT < 200, NA))
  return(dat)}

# Actually apply the preprocessing function
data_exp1 <- map_dfr(fnames_exp1, preproc_behav)

# Add factorized columns for participants and items (the random variables)
data_exp1 %<>% mutate(participant = as_factor(VPNummer), item = as_factor(StimID))

# Tabulate percentage of stimuli per condition
stims_exp1 <- table(data_exp1$participant, data_exp1$condition)
stims_exp1 <- colMeans(stims_exp1)
stims_exp1["Known"]/(3*120) # Three repititions and 120 objects
stims_exp1[c("Insight", "Naive")]/(3*60) # Three repitions and 60 objects each

# Import epochs from Python, converting Volts to Microvolts
epochs_exp1 <- py$epochs_exp1$get_data()*1e6

# Set rejected epochs to NA
rej_exp1 <- py$rej_exp1 + 1
epochs_exp1[rej_exp1,,] <- NA

@@

# Apply the function and bind ERPs to the behavioral data
data_exp1 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp1, els = els) %>% set_names(comps$name) %>% cbind(data_exp1, .)

# Remove trials with missing ERPs or RTs
rej_exp1_erp <- data_exp1 %>% filter(is.na(P1)) %>% count(participant, .drop = FALSE) %>% pull(n)
data_exp1 %<>% filter(!is.na(P1))
rej_exp1_rt <- data_exp1 %>% filter(is.na(RT)) %>% count(participant, .drop = FALSE) %>% pull(n)
data_exp1 %<>% filter(!is.na(RT))

# Remove any trials that don't beling to either of the two conditions
data_exp1 %<>% filter(condition != "Known") %>% droplevels()

# Set sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
t(contrasts.condition <- t(cbind(c("Insight" = 1, "Naive" = -1))))
t(contrasts.part <- t(cbind(c("1" = -1, "2" = 1, "3" = 0),
                            c("1" = 0, "2" = -1, "3" = 1))))
contrasts(data_exp1$condition) <- ginv(contrasts.condition)
contrasts(data_exp1$part) <- ginv(contrasts.part)

# Parameters for linear mixed-effects models (LMMs)
form <- tabulate.formula(~ part*condition + (part*condition|participant) + (part*condition|item))
form %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
ctrl_params <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

# Parameters for follow-up contrasts
specs = pairwise ~ condition|part

# Define function to compute LMMs and contrasts
compute_models <- function(dep, formula, data, control, specs){
  build <- buildmer(dep = dep, formula = formula, data = data, ddf = "Satterthwaite", calc.anova = TRUE, control = control)
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  conts <- emmeans(build@model, specs = specs, infer = TRUE)
  mod <- list("model" = build@model, "anova" = build@anova, "summary" = build@summary, "contrasts" = conts)
  return(mod)}

# Check if models were computed already (delete the file to re-run)
if (file.exists("output/exp1-stats.RDS")){
   # Load models from file
  models_exp1 <- readRDS("output/exp1-stats.RDS")
} else {
  # Actually apply the modelling function
  models_exp1 <- map(comps$name, compute_models, formula = form, data = data_exp1, control = ctrl_params, specs = specs) %>%
    set_names(comps$name)
  # Backup epochs to the export folder
  saveRDS(models_exp1, "output/exp1-stats.RDS")}
```

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

```{r setup, include=FALSE}
# Load packages
library(papaja)
library(reticulate)
library(MASS)
library(Matrix)
library(lme4)
library(lmerTest)
library(buildmer)
library(emmeans)
library(magrittr)
library(tidyverse)
library(cowplot)

# Chunk options
knitr::opts_chunk$set(include = FALSE, echo = FALSE, fig.out = "100%", fig.width = 10)

# Conda environment for Python
#use_condaenv("r-reticulate", required = TRUE)
renv::use_python(python = "/Users/alexander/opt/anaconda3/bin/python", type = "conda")

@@

```{r exp1-behavior}
# Function for processing behavioral data
preproc_behav <- function(txt_fname){
  # Read log file
  dat <- suppressMessages(suppressWarnings(read_tsv(txt_fname)))
  # Rename some columns
  dat %<>% rename(participant = VPNummer, item = StimID) %>%
    # Add a column for the part of the experiment
    mutate(part = as_factor(Wdh - min(Wdh) + 1)) %>%
    # Remove filler stimuli (i.e. well-known objects)
    filter(bek_unbek != "bekannt")
  # Assign stimuli to conditions based on keywords and button presses
  known <- dat %>% filter(part == "1" & Tastencode %in% c(201, 251)) %>% pull(item)
  insight <- dat %>% filter(part == "2" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
  naive <- dat %>% filter(part == "2" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
  # Create a new condition column, excluding trials with knwon stimuli or without condition
  dat %<>% mutate(condition = as_factor(case_when(item %in% known ~ "Excl_known",
                                                  item %in% insight ~ "Insight",
                                                  item %in% naive ~ "Naive",
                                                  TRUE ~ "Excl_cond")))
  # In Experiment 3, we need an additional column for position (upright vs. inverted)
  if("richtig_inv" %in% dat$Bed){
    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
      # Return only relevant columns
      select(part, position, condition, participant, item, RT)
  } else {
    dat %<>% select(part, condition, participant, item, RT)}
  return(dat)}

# Apply the preprocessing function
data_exp1 <- map(fnames_exp1, preproc_behav)

# Tabulate percentage of stimuli per condition
(stims_exp1 <- bind_rows(data_exp1) %>% filter(condition != "Excl_cond") %>% 
    group_by(participant, condition) %>% tally() %>%
    group_by(condition) %>% summarise(mean = mean(n)/(60*3)) %>% # 60 items per condition
    mutate(mean = if_else(condition == "Excl_known", mean/2, mean))) # 120 items in total
```

@@

# Define parameters for EEG preprocessing
preproc_params = dict(n_components=15, method='fastica',           # ICA parameters
                      l_freq=0.1, h_freq=30,                       # Filter edges
                      event_id={'match': 221, 'mismatch': 222},    # EEG triggers
                      tmin=-0.5, tmax=1.498,                       # Length of epochs
                      baseline=(-0.2,0),                           # Baseline correction
                      reject=dict(eeg=200e-6))                     # Rejection threshold

# # Debug
# locals().update(preproc_params)
# vhdr_fname = 'data/exp1/EEG/Vp0001.vhdr'
# metadata = metadata_exp1[0]

# Define preprocessing function
def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq, event_id, tmin, tmax, baseline, reject):
  # Load EEG data
  raw = mne.io.read_raw_brainvision(vhdr_fname, preload=True)
  # Create new virtual EOG channels
  raw = mne.set_bipolar_reference(raw, 'Auge_u', 'Fp1', ch_name='VEOG', drop_refs=False)
  raw = mne.set_bipolar_reference(raw, 'F9', 'F10', ch_name='HEOG', drop_refs=False)
  raw.set_channel_types(mapping={'VEOG': 'eog', 'HEOG': 'eog'})
  # Add EasyCap electrode layout, removing any excessive channels
  montage = mne.channels.make_standard_montage('easycap-M1')
  raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(['VEOG', 'HEOG'])))
  raw.set_montage(montage=montage)
  # Re-reference to common average
  raw, _ = mne.set_eeg_reference(raw, 'average')
  # Run ICA on a copy of the data
  filt_raw = raw.copy()
  filt_raw.load_data().filter(l_freq=1, h_freq=None)
  ica = mne.preprocessing.ICA(n_components=n_components, random_state=12345, method=method)
  ica.fit(filt_raw)
  # Remove bad components based on correlations with EOG
  eog_indices, eog_scores = ica.find_bads_eog(raw)
  ica.exclude = eog_indices
  raw = ica.apply(raw)
  # Apply band-pass filter
  raw = raw.filter(l_freq=l_freq, h_freq=h_freq)
  # Epoching including baseline correction
  events, _ = mne.events_from_annotations(raw, verbose=False)
  epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True)
  # Add behavioral data
  epochs.metadata = metadata
  # Reject bad epochs
  epochs = epochs.drop_bad(reject=reject)

  # # Autoreject                    
  # import autoreject
  # 
  # ar = autoreject.AutoReject(thresh_method='random_search', verbose=False)
  # epochs = ar.fit_transform(epochs)
  # 
  # ransac = autoreject.Ransac(verbose=False)
  # epochs = ransac.fit_transform(epochs)
  # 
  # reject = autoreject.get_rejection_threshold(epochs)
  # epochs = epochs.drop_bad(reject=reject)

@@

# Import behavioral data from R
metadata_exp1 = r.data_exp1

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists('output/exp1-epo.fif'):
  # Load preprocessed data from file
  epochs_exp1 = mne.read_epochs('output/exp1-epo.fif', preload=True)
else:
  # Apply the preprocessing function
  epochs_exp1 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp1, metadata_exp1)]
  # Combine epochs into a single data set
  epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
  # Backup epochs to the output folder
  epochs_exp1.save('output/exp1-epo.fif')

# # Get indices of bad epochs despite ICA
# rej_exp1 = epochs_exp1.drop_log
# rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
# rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]

# Define function to compute grand-averaged ERPs per condition
def compute_evokeds(epochs):
  evokeds = dict()
  evokeds_dat = dict()
  # Each part becomes a dictionary of conditions
  for pt in ['1', '2', '3']:
    evokeds['Pt' + pt] = dict()
    evokeds_dat['Pt' + pt] = dict()
    # Each condition becomes a list of participants
    for cn in ['Insight', 'Naive']:
      evokeds['Pt' + pt][cn] = list()
      evokeds_dat['Pt' + pt][cn] = list()
      # For every participant we average trials separately for all parts and conditions
      for vp in epochs.metadata['participant'].unique():
        query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
        evokeds['Pt' + pt][cn].append(epochs[query].average())
      # Compute grand averages across participants for this part and condition
      evokeds['Pt' + pt][cn] = mne.grand_average(evokeds['Pt' + pt][cn])
      # Export only the actual data for R
      evokeds_dat['Pt' + pt][cn] = evokeds['Pt' + pt][cn].data
  return(evokeds, evokeds_dat)

# Apply the function to compute grand averages
evokeds_exp1, evokeds_dat_exp1 = compute_evokeds(epochs=epochs_exp1)

# Export electrode positions for R
elpos = epochs_exp1._get_channel_positions()

# # Plot evoked potentials
# mne.viz.plot_compare_evokeds(evokeds=evokeds_exp1['Pt1'], picks='P8'); plt.show()
# mne.viz.plot_evoked_topomap(evoked=evokeds_exp1['Pt2']['Insight']-evokeds_exp1['Pt2']['Naive'])
# evokeds_exp1['Pt2']['Insight'].data = evokeds_exp1['Pt2']['Insight'].data - evokeds_exp1['Pt2']['Naive'].data
# evokeds_exp1['Pt2']['Insight'].plot_topomap(times=[0.125, 0.175, 0.5], average=0.05, vmin=-1, vmax=1, cmap='viridis'); plt.show()
```

```{r exp1-analysis}
# Re-import behavioral data
data_exp1 <- py$epochs_exp1$metadata

# Factorize some columns
data_exp1 %<>% mutate(part = factor(part, levels = c("1", "2", "3")),
                      condition = factor(condition, levels = c("Insight", "Naive", "Excl_known", "Excl_cond")),
                      participant = factor(participant), item = factor(item))

# Check number of rejected epochs
rejected_exp1 <- data_exp1 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
mean(rejected_exp1); median(rejected_exp1); range(rejected_exp1)

@@

# Check if ERPs were computed already (delete the file to re-run)
if (file.exists("output/exp1-erps.RDS")){
  # Load ERPs from file
  data_exp1 <- readRDS("output/exp1-erps.RDS")
} else {
  # Import epochs from Python, converting Volts to Microvolts
  epochs_exp1 <- py$epochs_exp1$get_data()*1e6
  # Apply the ERP function and save to output folder
  data_exp1 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp1, els = els) %>%
    set_names(comps$name) %>% cbind(data_exp1, .) %T>% saveRDS("output/exp1-erps.RDS")}

# Remove any trials that don't beling to either of the two conditions
data_exp1 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()

# Sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
t(contrasts_condition <- t(cbind(c("Insight" = 1, "Naive" = -1))))
t(contrasts_part <- t(cbind(c("1" = -1, "2" = 1, "3" = 0),
                            c("1" = 0, "2" = -1, "3" = 1))))
contrasts(data_exp1$condition) <- ginv(contrasts_condition)
contrasts(data_exp1$part) <- ginv(contrasts_part)

# Formula and parameters for linear mixed-effects regression models (LMMs)
form_exp12 <- tabulate.formula(~ part*condition + (part*condition|participant) + (part*condition|item))
form_exp12 %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
ctrl_params <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

# Formula for follow-up contrasts
specs_exp12 = pairwise ~ condition|part

# Define function to compute LMMs and contrasts for each component
compute_models <- function(dep, formula, data, control, specs){
  browser()
  build <- buildmer(dep = dep, formula = formula, data = data, ddf = "Satterthwaite", calc.anova = TRUE, control = control)
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts %>% as.data.frame()
  mod <- list("model" = build@model, "anova" = build@anova, "summary" = build@summary, "contrasts" = conts)
  return(mod)}

# Check if models were computed already (delete the file to re-run)
if (file.exists("output/exp1-stats.RDS")){
  # Load models from file
  models_exp1 <- readRDS("output/exp1-stats.RDS")
} else {
  # Apply the modelling function and save to output folder
  models_exp1 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp1, control = ctrl_params,
                     specs = specs_exp12) %>% set_names(comps$name) %T>% saveRDS("output/exp1-stats.RDS")}

# Store significance levels for plotting
stars_exp1 = list(P1 = c(Pt1 = NA, Pt2 = NA, Pt3 = "*"),
                  N1 = c(Pt1 = NA, Pt2 = "**", Pt3 = NA),
                  N400 = c(Pt1 = NA, Pt2 = "***", Pt3 = "**"))
```

```{r exp1-table, include=TRUE, results="asis"}
# Check if models were computed already (delete the file to re-run)
if (file.exists("output/exp1-stats.RDS")){
  # Load models from file
  models_exp1 <- readRDS("output/exp1-stats.RDS")
} else {
  # Apply the modelling function and save to output folder
  models_exp1 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp1, control = ctrl_params,
                     specs = specs_exp12) %>% set_names(comps$name) %>% saveRDS("output/exp1-stats.RDS")}

# Define function to create ANOVA-style table
create_table <- function(models, stub.anova, stub.contrasts, caption, note){
  anov <- map(models, function(model){
    data.frame("stat" = paste0(format(round(model$anova$`F value`, 2), trim = FALSE, nsmall = 2), " (", model$anova$NumDF,
                               ", ", format(round(model$anova$DenDF, 1), trim = FALSE, nsmall = 1), ")"),
               "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)) %>%
      mutate(p = ifelse(p == "0.000", "<.001", substr(p, 2, nchar(p))))}) %>%
    bind_cols() %>% set_rownames(c(stub.anova))
  cnames <- c("\\textit{Type III}", rep(c("\\textit{F} (\\textit{df})", "p" = "\\textit{p}"), 3))
  conts <- map(models, function(model){
    data.frame("stat" = paste0(format(round(model$contrasts$estimate, 2), trim = FALSE, nsmall = 2), " [",
                               format(round(model$contrasts$lower.CL, 2), trim = FALSE, nsmall = 2), ", ",
                               format(round(model$contrasts$upper.CL, 2), trim = FALSE, nsmall = 2), "]"),
               "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)) %>%
      mutate(p = ifelse(p == "0.000", "<.001", substr(p, 2, nchar(p)))) %>%
      add_row("stat" = "Est. [95% CI]", "p" = "\\textit{p}", .before = 1)}) %>% 
    bind_cols() %>% set_rownames(c("\\textit{Insight $-$  naive}", stub.contrasts))
  apa_table(list(anov, conts), col.names = cnames, escape = FALSE,
            col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N1}" = 4:5, "\\textbf{N400}" = 6:7),
            midrules = c(nrow(anov) + 1), font_size = "footnotesize", align = "lcccccc",
            caption = caption, note = note)}

# Apply the function to print the table
create_table(models_exp1, stub.anova = c("Part", "Insight", "Pt. × ins."),
             stub.contrasts = c("Part 1", "Part 2", "Part 3"),
             caption = "Results of linear mixed-effects regression models for Experiment 1",
             note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
```

```{r exp1-plotting, include=TRUE, fig.height=12}
# Import grand averaged evoked potentials from Python
evokeds_exp1 <- py$evokeds_dat_exp1

# Retrive locations for the relevant electrodes from standard montage
montage <- py$evokeds_exp1$Pt1$Insight$ch_names %>% as_tibble() %>% rename(electrode = value) %>%
  left_join(read.delim("renv/python/condaenvs/renv-python/lib/python3.8/site-packages/mne/channels/data/montages/easycap-M1.txt") %>% 
              as_tibble() %>% rename(electrode = Site)) %>%
  mutate(x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
         y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)))

# Define function to plot trial structure
plot_trial <- function(){
  colour_insight <- viridisLite::viridis(1, begin = 0, end = 0)
  colour_naive <- viridisLite::viridis(1, begin = 0.5, end = 0.5)
  trial_pt1 <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
    geom_text(aes(x = 37, y = 68, label = "Part 1"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
    draw_image("materials/exp1/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica") +
    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
  trial_pt2 <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
    geom_text(aes(x = 37, y = 68, label = "Part 2"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
    geom_rect(aes(xmin = 0, xmax = 20, ymin = 0, ymax = 20), color = "black", fill = "white") +
    geom_text(aes(x = 10, y = 10.5, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
    geom_text(aes(x = 10, y = -3, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = colour_insight, fill = "white") +
    geom_text(aes(x = 28, y = 23, label = "Potato\nmashing"), color = colour_insight, size = 10/.pt, family = "Helvetica") +
    geom_text(aes(x = 28, y = 10, label = "2.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
    geom_rect(aes(xmin = 18, xmax = 38, ymin = 39, ymax = 59), color = colour_naive, fill = "white") +
    geom_text(aes(x = 28, y = 49, label = "Message\nmorsing"), color = colour_naive, size = 10/.pt, family = "Helvetica") +
    geom_text(aes(x = 28, y = 36, label = "or"), color = "black", size = 10/.pt, family = "Helvetica") +
    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
    geom_text(aes(x = 46, y = 34, label = "*"), size = 8, family = "Helvetica") +
    geom_text(aes(x = 46, y = 23, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
    geom_rect(aes(xmin = 54, xmax = 74, ymin = 39, ymax = 59), color = "black", fill = "white") +
    draw_image("materials/exp1/potato_masher.png", x = 54, y = 39, width = 20, height = 20) +
    geom_text(aes(x = 65, y = 36, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica", lineheight = 1) +
    geom_segment(aes(x = 28, y = 0, xend = 74, yend = 33.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
  trial_pt3 <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
    geom_text(aes(x = 37, y = 68, label = "Part 3"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
    draw_image("materials/exp1/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica") +
    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
  plot_grid(trial_pt1, NULL, trial_pt2, NULL, trial_pt3, nrow = 1, rel_widths = c(10, 1, 10, 1, 10))}

# Define function to plot mean ERP amplitudes
plot_bars <- function(data, stars, ymin){
  parts <- map(unique(data$part), function(part){
    # For which components in the current part do we have a significant effect?
    sig <- map(stars, paste0("Pt", part)) %>% as.data.frame() %>% t() %>% as.data.frame() %>%
      set_colnames("label") %>% rownames_to_column("comp") %>% na.omit()
    # Create bar plot for the current part
    map(c("P1", "N1", "N400"), function(comp){
      p <- data %>% filter(part == !!part) %>%
        Rmisc::summarySEwithin(measurevar = comp, withinvars = "condition", idvar = "participant") %>%
        mutate(comp = !!comp) %>% rename(amplitude = !!comp)}) %>% bind_rows() %>%
      mutate(comp = fct_relevel(comp, "P1", "N1", "N400")) %>%
      ggplot(aes(x = comp, y = amplitude, fill = condition)) +
      # geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
      # annotate("tile", x = sig$comp, y = -0.4, width = 0.45, height = 0.8, colour = "black", fill = "white", size = 0.5) +
      # annotate("rect", xmin = -Inf, xmax = Inf, ymin = -0.2, ymax = Inf, fill = "white") +
      # geom_bar(aes(y = amplitude - se - 0.2), stat = "identity", position = position_dodge()) + scale_fill_manual(values = c("white", "white")) +
      # new_scale_fill() +
      # annotate("label", x = sig$comp, y = -0.96, label = sig$label, size = 7, family = "Helvetica", label.size = 0) +
      geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
      scale_fill_viridis_d(end = 0.5) +
      geom_errorbar(aes(ymin = amplitude - se, ymax = amplitude + se), position = position_dodge(width = 0.9), width = 0.5) +
      annotate("text", x = sig$comp, y = ymin, label = sig$label, size = 6, family = "Helvetica") +
      geom_hline(yintercept = 0) +
      coord_cartesian(ylim = c(ymin, ymin + 7)) +
      ylab("ROI ampl.\n(µV)") +
      scale_y_continuous(breaks = seq(trunc(ymin), trunc(ymin) + 6, 2)) +
      theme_classic() +
      theme(legend.position = "none",
            panel.grid = element_blank(),
            axis.ticks = element_line(color = "black"),
            axis.title.x = element_blank(),
            axis.title.y = element_text(family = "Helvetica", color = "black", size = 10),
            axis.text = element_text(family = "Helvetica", color = "black", size = 10),
            plot.margin = margin(t = 0.3, r = 0, b = 0.4, l = 0.2, "cm"))})
  plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))}
